---
title: "esm206-lab10-key"
author: "Katie Munster"
date: "11/30/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(usethis)
library(janitor)

# New packages:
library(beepr)
library(praise)
library(cowsay)
library(paletteer)
library(sf)
```

## beepr beeps

Use the function `beep()` in the beepr package to make an audio alert when your code is done running.

```{r, eval = FALSE}
for(i in rev(seq(1:9999))) {
  print(paste(i, "bottles of beer on the wall"))
}

# beep(4)
```

## praise and cowsay

Packages built wiht a single purpose: to be kind and fun.

```{r}
praise("${Exclamation}, ${EXCLAMATION}...${exclamation}!!!!")

praise("Holy ${creating}, Batman - this code is ${ADJECTIVE}!")
```

Use cowsay::say() to make a character say something to you.

# usethis::edit_r_profile()



To connect to git in the console:
# usethis::use_git()

# usethis::use_github()

in the terminal:

git branch -m master main
git fetch origin
git branch -u origin/main main
git remote set-head origin -a


## paletteer to access thousands of color palettes

```{r}
storms %>% 
  group_by(name) %>% 
  summarize(min_pressure = min(pressure, na.rm = TRUE)) %>% 
  slice_min(n = 10, min_pressure) %>% 
  ggplot(aes(x = min_pressure, y = name)) +
  geom_col(aes(fill = name)) +
  scale_fill_paletteer_d("ggsci::pink_material")
# View(palettes_d_names) in the console to see colors
# paletteer_d("palettetown::miltank") in console to see the exact color codes
```






